Compiling list of medications based on BNF codes for dementia/AD & palliative care drugs

### 2023-01-30 compile_medications_from_bnf.Rmd
I've included a list of medicines for polypharmacy definitions, reading it using docxtractor::read_docx(); this doesn't work with a downloaded file but can read straight from the URL! needed to specify path to LibreOffice binary for it to work

@@

```{r}
library(tidyverse)
library(readxl)  # for loading excel files
library(janitor)  # for cleaning data
library(knitr)  # for pretty tables in the report
```

@@

@@

@@

@@

>>>>

## List of discrete medications

To count the number of different prescriptions or measure polypharmacy, we need to define discrete medications that can be prescribed/dispensed, whilst removing things like dressings, vaccines, etc.

[Guthrie et al., 2015 ("The rising tide of polypharmacy and drug-drug interactions: population database analysis 1995–2010")](https://doi.org/10.1186/s12916-015-0322-7) define this in their Additional file, table S1, which I'll copy-paste and export as .csv below.

@@

```{r}
library(tidyverse)
library(readxl)  # for loading excel files
library(janitor)  # for cleaning data
library(knitr)  # for pretty tables in the report
library(docxtractr)  # for reading data from table in .docx file
```

@@

## BNF codes

@@

## List of medicines

Note: there appears to be an error with using `docxtractor::read_docx()` with a file downloaded to OneDrive; reading directly from the URL works fine, however! Therefore I've skipped downloading the file below.

```{r}
url_medicines <- "https://static-content.springer.com/esm/art%3A10.1186%2Fs12916-015-0322-7/MediaObjects/12916_2015_322_MOESM1_ESM.doc"

# path_medicines <- file.path("./bnf", basename(url_medicines))
# download.file(url = url_medicines, destfile = path_medicines)
```

@@

## List of medicines

```{r}
# doc <- read_docx(path_medicines)
## error with reading from OneDrive folder?
doc <- read_docx(url_medicines)
extracted_table <- 
  docx_extract_tbl(doc, 1)
```

@@

## Discrete medicines from Guthrie et al., 2015 paper

```{r}
# TODO: process this if needed?
medicines_list <- 
  extracted_table %>%
  clean_names() %>%
  mutate(
    chapter = as.integer(str_extract(drug_class_name, pattern = "(?<=Chapter )\\d+"))
  ) %>%
  filter(bnf_subsection!="") %>%
  fill(chapter, .direction = "down")
```
